Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-21 paper/paper.tex
#25 get equation 2 right
#25 push overleaf changes

Since the outcome is binary, equation \ref{eq:sw22} represents a linear probability model: we model $construction_{it}$ as a random variable that follows a Bernoulli distribution with a probability parameter $p$ that is conditional on the right-hand side variables. This way we can interpret the values of coefficients as differences in the probability of recorded construction activity in a given period.

@@

I switch to a simple difference-in-differences specification for clarity. I extend the previous regression by interacting with the type of the ownership change:

\begin{equation}
\label{eq:baseline}
    construction_{it} = \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0)\beta +
    \mathbf{1}(t \ge e^{NewState}_i)\pi +
    \mathbf{1}(t \ge e^{NewState}_i) T_i \theta + \varepsilon_{it}
\end{equation}

@@

\subsection*{Tables}

\input{paper/output/regressions/SW22_replication_50y}

@@

\clearpage
\subsection*{Figures}

\begin{figure}
    \centering
    \includegraphics[scale = 0.4]{paper/output/regressions/SW22_replication_50y.png}
    \caption{It looks just like it's supposed to!}
    \label{fig:SW_replication}
\end{figure}

>>>>

Since the outcome is binary, equation \eqref{eq:sw22} represents a linear probability model: we model $construction_{it}$ as a random variable that follows a Bernoulli distribution with a probability parameter $p$ that is conditional on the right-hand side variables. This way we can interpret the values of coefficients as differences in the probability of recorded construction activity in a given period.

@@

I switch to a simple difference-in-differences specification for clarity. I extend the previous regression by interacting with the type of the ownership change:
\begin{equation}
\label{eq:baseline}
\begin{split}
    construction_{it} &= \alpha_i + \delta_t + \mathbf{1}(S_{it} > 0)\beta +
    \mathbf{1}(t \ge e^{NewState}_i)\pi \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Switch Type = conquest) \times \theta_{conquest} \\
    &+ \mathbf{1}(t \ge e^{NewState}_i) \times
    \mathbf{1}(Switch Type = other) \times \theta_{other} + \varepsilon_{it}
\end{split}
\end{equation}

with the only addition being $T_i$, which denotes the type of switch that brought the new state into power. I distinguish three different categories of switches: conquests, successions, and other. In the above regression, successions are the omitted category. The coefficient of interest is the

@@

\subsection*{Figures}

\begin{figure}[ht]
    \centering
    \includegraphics[scale = 0.4]{paper/output/regressions/SW22_replication_50y.png}
    \caption{It looks just like it's supposed to!}
    \label{fig:SW_replication}
\end{figure}

\clearpage
\subsection*{Tables}

% \input{paper/output/regressions/SW22_replication_50y}

@@
